\documentclass{article} 
\usepackage[margin=0.8in]{geometry}
\usepackage{color}

\newcommand{\eq}[1]{\begin{equation}{#1}\end{equation}}
\newcommand{\clred}[1]{\textcolor{red}{#1}}

\begin{document}
\large{
\section*{Meeting Notes: May 30, 17}
% Based on daily log notes for May 30, 17
Overall goal: calculate cross-correlations between CMB lensing and LSS.
\begin{itemize}
\item Want $C_\ell^{\kappa\kappa}$ which probes $\sigma_8^2$; $C_\ell^{\kappa g}$ which probes $b\sigma_8^2$; $C_\ell^{gg}$ which probes $b^2\sigma_8^2$.
	\begin{itemize}
	\item Since deal with galaxies in specific redshift bins, explicitly consider auto- and cross-spectra for the bins.
	\item Say $i$th $z$-bin has central redshift $z_i$. Adopt the convention of writing the cross spectrum as $C_\ell^{\kappa i}$ which probes $b(z_i) \sigma_8^2(z_i)$ and $C_\ell^{ii}$ which probes $b^2(z_i)\sigma_8^2(z_i)$. \clred{Should $\sigma_8$ have the $z$-dependence? If yes, if/how does $z$-bin dependence come in through $C_\ell^{\kappa\kappa}$?}
	\end{itemize}
\item Expect coupled systematics due to dust uncertainties to be the biggest source of problems. Need to look at cross-correlations between CMB lensing and dust uncertainties.
\item Will need to think about two kinds of dust contributions: 1) MW dust extinguishes background galaxies; its microwave emission affects lensing, and 2) CIB affects lensing and hence correlates with galaxy distribution.
\end{itemize}

% Plan
% kappa
\subsection*{Convergence Field}
Know
\eq{\kappa(x)= \int_0^\infty dz W^c(z)\delta(x,z) \label{eq: kappa}}
where $W^c(z)$ is the CMB window function, $\delta(x,z)$ is the matter density field, and $x$ is the position on the sky.

Now, since we have LSS for different redshift bins and hence have $\delta(x, z)$ in Equation~\ref{eq: kappa}, we can break $\kappa(x)$ as contributions from different redshift bins:
\eq{\kappa(x)= \int_0^{z_1} dz W^c(z)\delta(x,z) + \int_{z_1}^{z_2} dz W^c(z)\delta(x,z) + ... + \int_{z_n}^\infty dz W^c(z)\delta(x,z) \label{eq: kappa break}}

We can choose redshift bins such that the CMB window function $W^c(z)$ can be approximated as a top-hat in the given bin (with central redshift $z_i$). Then we have
\eq{\kappa(x)= \sum_{i=1}^n W(z_i)\delta(x,z_i) +  \int_{z_n}^\infty dz W^c(z)\delta(x,z) \label{eq: kappa break}}
where the last integral needs to be evaluated in full since neither $W^c(z)$ nor $\delta(x,z) $ is a constant for any broad $z$-bin.

% cross correlation
\subsection*{Cross-Correlations}
In Limber approximation, the cross-correlation can be written in closed form as
\eq{C_\ell^{\kappa g}= \int_0^\infty dz W^g(z)W^c(z)b(z)P^{true}_\ell(k, z) \label{eq: C-cross}}
where $W^g(z)$ is the LSS window function, $W^c(z)$ is the CMB window function and $P^{true}_\ell(k, z)$ is the true matter power spectrum as a function of redshift.

% OS induced power
\subsection*{Observed Power Spectrum}
We can use Equation~\ref{eq: C-cross} to incorporate the effects of artifacts induced in the observed matter power spectrum. For instance, we know From Awan+ 2016 and LSST Observing Strategy White Paper that
\eq{P^{obs}_\ell(k, z)= W_\ell^2 P^{true}_\ell(k, z) + P^{OS}_\ell(k, z) \label{eq: Pobs}}
where $W_\ell$ is the survey window function.

% Plan
\subsection*{Plan}
\begin{itemize}
\item Use CAMB to get $P(k,z)$. \clred{Does it give $P_l(k,z)$? Otherwise, how to calculate?}
\item Use  $P_\ell(k,z)$ to realize $\delta(x, z)$. 
\item Find the convergence field using Equation~\ref{eq: kappa break}; will need $W^c(z)$. Find $C_\ell^{\kappa\kappa}$.
\item Find $C_\ell^{ii}$ using the realized $\delta(x,z)$.
\item Find $C_\ell^{\kappa i}$ using Equation~\ref{eq: C-cross}. For $W^g$, start with assuming its a top-hat in each $z$-bin.
\item Give synfast $C_\ell^{\kappa\kappa}, C_\ell^{\kappa i}, C_\ell^{ii}$ as the TE fields, which will return a realization of the convergence and density fields as maps.
\item Cross-correlate the maps.
\item Add OS artifacts to the realized map of LSS. These artifacts are calculate using LSST MAF pipeline.
\item Dust artifacts will need to be added to both the convergence and LSS maps. 
\item Cross-correlate the with-artifacts maps to see the amount of spurious power.
\end{itemize}

% To-Do
\subsection*{To-Do Before Simons Summer Meeting}
Goal: have CMB lensing-LSS correlation by Simons meeting (with a simple handle on dust).
\begin{itemize}
\item Humna: Look at Baxter+ (SPT/DES), Miyatake+ (Planck/CMASS), Schaan et al.
\item Humna: Set up CAMB.
\item Mat: Provide $W^c(z)$.
\item Humna: Run LSST OS artifacts pipeline at Nside= 1024. No need to get higher-$z$ spectra from Hu as wont be using his data as true LSS but CAMB's. Nelson's mock catalogs have high-$z$ spectra so need to incorporate them to calculate the artifacts for all relevant redshift bins.
\item All: Do a literature review to see what has been done in the field so far.
\end{itemize}









}
\end{document}